\pkg{sdmTMB}: An \proglang{R} Package for Fast, Flexible, and User-Friendly Generalized Linear Mixed Effects Models with Spatial and Spatiotemporal Random Fields

### 2023-12-13 doc/paper-jss/sdmTMB-paper.Rnw
typo

To do this, we use counts of Snowy Owls observed by the annual Christmas Bird Counts \citep{cbc} from all locations where they have been recorded and for which there were at least three counts conducted between 1979 and 2020.
Our data are read from supplementary data and also contain columns for spatial coordinates (in an Albers projection for North America and divided by 100000 to give units of 100 km), year, year as a factor, the annual NAO value, and own count:

>>>>

To do this, we use counts of Snowy Owls observed by the annual Christmas Bird Counts \citep{cbc} from all locations where they have been recorded and for which there were at least three counts conducted between 1979 and 2020.
Our data are read from supplementary data and also contain columns for spatial coordinates (in an Albers projection for North America and divided by 100000 to give units of 100 km), year, year as a factor, the annual NAO value, and owl count:
